PrepCAISOData

### 2014-12-17 CAData/CAISO/LoadData.Rmd
Seeing how the forecasts and actuals compare.

```{r}
setwd("/home/woodsj/Research/Forecast-Peak-With-Google-Trends/CAData/CAISO")
# Get the files names
files <- list.files(pattern="*.csv")

@@

>>>>

```{r}
OldWD<-getwd()
setwd("/home/woodsj/Research/Forecast-Peak-With-Google-Trends/CAData/CAISO")
# Get the files names
files <- list.files(pattern="*.csv")

@@

Now lets sort out how the 7day ahead market is related to the actual

CAISOWorking$Hour<-as.factor(CAISOWorking$OPR_HR)
#line up actual and 7day with the time in the line

Forecast<-CAISOWorking[CAISOWorking$MARKET_RUN_ID=="7DA",]
Actual<-CAISOWorking[CAISOWorking$MARKET_RUN_ID=="ACTUAL",]

library(sqldf)
sqldf("select * from Actual;")

sqldf("select Actual.Hour, Actual.OPR_DT, Actual.MW as Actual, Forecast.MW as Forecast from Forecast, Actual where Actual.Hour=Forecast.Hour and Actual.OPR_DT=Forecast.OPR_DT;")

table(CAISOWorking$INTERVALSTARTTIME_GMT)

#line up acutal with 7day from seven days before.

```
